Sample size

### 2021-04-15 scripts/r/sample-size/sample-size.Rmd
add save sample_sims

```{r run-sims}
sample_sims <- tibble(
  n_teams = n_ts_qs$n_teams,
  quants = n_ts_qs$quantiles,
  models = map2(
    n_teams, quants,
    ~run_simulations(.x, .y)
  )
)
```

>>>>

```{r run-sims}
sample_sims <- tibble(
  n_teams = n_ts_qs$n_teams,
  quants = n_ts_qs$quantiles,
  models = map2(
    n_teams, quants,
    ~run_simulations(.x, .y)
  )
)

saveRDS(sample_sims, "./models/sims/sample_sims.rds")
```
